On Secure Delegation of SampBQP with a Classical Client

### 2020-02-07 bqp.tex
Add more Skype discussion notes

@@

\begin{protocol}{1-message $\QPIP_1$ protocol for $\BQP$}
	\label{proto:BQP}
	Let $L\in\BQP$, and $x\in\set{0,1}^n$. Let $m=\poly(n)$
	\begin{enumerate}
		\item On input $L$ and $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_{L, x}$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is single-qubit $X$ or $Z$ measurements.
		\item The verifier sends $x$ to the prover.
		\item The prover applies a certain CPTP $\cF$ on $x$ to generate $\rho\in\cB^{\otimes m}$.
			\Ethan{Now we need to define CPTP in prelim...}
		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $w$.
		\item The verifier runs some $\BPP$ algorithm $\cV$ on input $w$ and outputs either accept or reject.
	\end{enumerate}
\end{protocol}

We compile this protocol using $\mathsf{QHE}$ to obtain a blind 1-message $\QPIP_1$ protocol for $\BQP$, again with only $X$ and $Z$ measurements.
The high level idea is to run \cref{proto:BQP} under $\mathsf{QHE}$.
Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
The prover then homomorphically evaluate $\cF$ on $y$ to produce $\sigma=\mathsf{QHE.Enc}(\rho)$ \Ethan{Is this actually ok? $\sigma$ is a ciphertext corresponding to $\rho$, but it wasn't encrypted. In fact it's deteriorated due to homomorphic eval} and send it back to the verifier.

@@

	There exists $\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$ where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and $\BPP$ algorithm $\widehat{\mathsf{QHE.Dec}}$ such that:
	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{thm}
\begin{proof}
	This is a proof by construction.
	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$

@@

	Let $\Lambda'$ applies $\Lambda$ to the first register, getting $ct=\Lambda(X^xZ^z\rho Z^zX^x)$, and applies computational basis measurement to the second register, getting $c_{x, z}$.

	Note that the Pauli one-time pad on $ct$ commutes with $X$ and $Z$ measurements.
	So let $\widehat{\mathsf{QHE.Dec}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $ct$ to get $\Lambda(\rho)$.
\end{proof}

@@

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $x\in\set{0,1}^n$.
	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cF$.
	Take $\pi_{L, x}$, $\cF$, and $\cV$ to be the same as in \cref{proto:BQP}
	\begin{enumerate}
		\item The verifier samples $\Lambda$ from $\pi_{L, x}$
		\item The verifier computes $\Lambda'$ using \cref{decodeMeasureOrder}
		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
		\item The verifier computes $y=\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $y$ and $evk$ to the prover
		\item The prover computes $\sigma=\mathsf{QHE.Eval}(\cF, y)$
		\item The prover sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming ciphertext according to $\Lambda'$, getting $ct$
		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $w$.
		\item The verifier applies $\cV$ to $w$ and outputs its result.
	\end{enumerate}
\end{protocol}

@@

@@

@@

\cite{mahadev_delegation} gives a compiler from $\QPIP_1$ protocols of the form in \cref{proto:BQP} to $\QPIP_0$ but deteriorates soundness.
Note that \cref{proto:BlindBQP} can also be collapsed into the same form, so the same compiler can also be applied to it to obtain a $\QPIP_0$ protocol.

@@

>>>>

\Ethan{Cut into two subsections, one for BQP and one for FBQP}

@@

\begin{protocol}{1-message $\QPIP_1$ protocol for $\BQP$ language $L$}
	\label{proto:BQP}
	Input: $x\in\set{0,1}^n$.
	\Ethan{Consider more notation $V_1$, $P_2$... See parallel rep paper. Numbering like this works better for compilers}
	\Ethan{Use terms like ``generate" or arrows; see google docs}
	\begin{enumerate}
		\item On input $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_x$, where $m=\poly(n)$, $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
		\item The verifier sends $x$ to the prover.
		\item The prover applies an algorithm $\cF$ \Ethan{Probably P3 or maybe a ``meaningful" name} on $x$ to generate $\rho\in\cB^{\otimes m}$.
		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $w$.
		\item The verifier runs some polynomial-time algorithm $\cV$ on input $w$ and outputs either accept or reject.
	\end{enumerate}
\end{protocol}

We compile this protocol using Mahadev's $\mathsf{QHE}$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol for $\BQP$, again with only $X$ and $Z$ measurements.
The high level idea is to run \cref{proto:BQP} under $\mathsf{QHE}$.
Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
The prover then homomorphically evaluate $\cF$ on $y$ to produce $\sigma=\mathsf{QHE.Enc}(\rho)$ \Ethan{Is this actually ok? $\sigma$ is a ciphertext corresponding to $\rho$, but it wasn't encrypted. In fact it's deteriorated due to homomorphic eval} and send it back to the verifier.

@@

	There exists $\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$ where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and polynomial-time algorithm $\widehat{\mathsf{QHE.Dec}}$ such that:
	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{thm}
\begin{proof}
	This is a proof by construction.
	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$

@@

	Let $\Lambda'$ applies $\Lambda$ to the first register, getting $u=\Lambda(X^xZ^z\rho Z^zX^x)$, and applies computational basis measurement to the second register, getting $c_{x, z}$.

	Note that the Pauli one-time pad on $u$ commutes with $X$ and $Z$ measurements.
	So let $\widehat{\mathsf{QHE.Dec}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $u$ to get $\Lambda(\rho)$.
\end{proof}

@@

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $x\in\set{0,1}^n$.
	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cF$.
	Take $\pi_{L, x}$, $\cF$, and $\cV$ to be the same as in \cref{proto:BQP}
	\begin{enumerate}
		\item The verifier samples $\Lambda$ from $\pi_{L, x}$
		\item The verifier computes $\Lambda'$ using \cref{decodeMeasureOrder}
		\item The verifier computes $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$.
		\item The verifier computes $y=\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $y$ and $evk$ to the prover
		\item The prover computes $\sigma=\mathsf{QHE.Eval}(\cF, y)$
		\item The prover sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming ciphertext according to $\Lambda'$, getting $ct$
		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $w$.
		\item The verifier applies $\cV$ to $w$ and outputs its result.
	\end{enumerate}
\end{protocol}

@@

\Ethan{Combine the following two theorems}

@@

    \Ethan{rewrite the following as a reduction. If exists adversary $P*$ that breaks soundness of this protocol, it breaks the other one...}

@@

\Ethan{Use google docs to replace below}

\cite{mahadev_delegation} gives a compiler from $\QPIP_1$ protocols of the form in \cref{proto:BQP} to $\QPIP_0$ but deteriorates soundness.
Note that \cref{proto:BlindBQP} can also be collapsed into the same form \Ethan{Actually specify QPIP1 one-message use only XZ measurements}, so the same compiler can also be applied to it to obtain a $\QPIP_0$ protocol.

@@

\Ethan{Need more notation}

### 2020-02-07 preliminaries.tex
Add more Skype discussion notes

@@

The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
	\item Its ciphertext takes the form $(X^xZ^z\ket\rho Z^zX^x, c_{x, z})$, where $\rho$ is the plaintext and $c_{x, z}$ is a ciphertext that decodes to $(x, z)$ under a certain classical homomorphic encryption scheme.
	We assume without loss of generality that the length of $c_{x, z}$ is only dependent on the length of $\ket\phi$ by padding $0$s if necessary.
\end{itemize}

>>>>

\begin{definition} [$\FBQP$]
	TODO copy from https://www.csa.iisc.ac.in/~chandan/courses/complexity15/notes/lec23.pdf and add in overwhelming prob.
\end{definition}

@@

The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
	\item Its ciphertext takes the form $(X^xZ^z\rho Z^zX^x, c_{x, z})$, where $\rho$ is the plaintext and $c_{x, z}$ is a ciphertext that decodes to $(x, z)$ under a certain classical homomorphic encryption scheme.
\end{itemize}
